INTELLIGENT SYSTEMS

### 2021-03-31 paper_3.tex
finish 3.3.3

\subsubsection{Learning Algotrithm}
In order for both networks to have good training, their parameters must be 
optimized (weights and bias). To achieve this, the following formulas will 
have to be optimized iteratively:
\begin{equation}
    \hat{\theta_1} = \argmin\limits_{\theta_1}||Re(\hat{\theta_2},Cr(\theta_1,x))-x||^2
\end{equation}
\begin{equation}
    \hat{\theta_2} = \argmin\limits_{\theta_2}||Re(\hat{\theta_2},\hat{x}_m)-x||^2
\end{equation}
Where:
\begin{enumerate}
    \item \emph{x} represents the original image
    \item $ \hat{\theta_1} $ and $ \hat{\theta_2} $ are the parameters of \emph{ComcCNN} and \emph{RecCNN}
    \item $ C_r(\cdot) $ and $ R_e() $ represent the \emph{ComcCNN} and \emph{RecCNN}
\end{enumerate}

\subsubsection{Loss Functions}

>>>>

\subsubsection{Learning Algotrithm}
In order for both networks to have good training, their parameters must be 
optimized (weights and bias). To achieve this, the following formulas will 
have to be optimized iteratively:
\begin{equation}
    \hat{\theta_1} = \argmin\limits_{\theta_1}||Re(\hat{\theta_2},Cr(\theta_1,x))-x||^2
\end{equation}
\begin{equation}
    \hat{\theta_2} = \argmin\limits_{\theta_2}||Re(\hat{\theta_2},\hat{x}_m)-x||^2
\end{equation}
Where:
\begin{itemize}
    \item \emph{x} represents the original image
    \item $ \hat{\theta_1} $ and $ \hat{\theta_2} $ are the parameters of \emph{ComcCNN} and \emph{RecCNN}
    \item $ C_r(\cdot) $ and $ R_e() $ represent the \emph{ComcCNN} and \emph{RecCNN}
    \item $ \hat{x}_m $ is th e decoded compact representation of \emph{x}
\end{itemize}

\subsubsection{Loss Functions}
For ComCNN training: as a loss function, we use the mean square error (\emph{MSE}):
\begin{equation}
    L_1(\theta_1) = \frac{1}{2N}\sum_{k=1}^N||Re(\hat{\theta_2}, C_r(\theta1,x_k))-x_k||^2
\end{equation}
Where \emph{N} and $ \theta_1 $ represent the batch size and the trainable parameter.
For REcCNN training: after obtaining a set of compact $ x_m $ images from 
\emph{ComCNN} and the original \emph{x} images, we also use the mean square error 
(\emph{MSE}) here:
\begin{equation}
    L_2(\theta_2) = \frac{1}{2N}\sum_{k=1}^N||res(Co(\hat{x}_{mk}), \theta_2) - (Co(\hat{x}_{mk})-x_k)||^2
\end{equation}
Where $ \theta_2 $ are the trained parameters of the network while $ res(\cdot) $ represent 
the residual learning of the \emph{RecCNN}.
